Project Report\\\textsc{DEVS Ex Machina}

### 2015-05-18 manual/projectrapport.tex

\section{Messaging Size}
A message is constructed once, and after that never copied. Messages are sent and received by reference to smart pointer, incurring a size cost of (on 64-bit platforms) 128bit. The payload (and its size) is irrelevant to the simulation up to the point where the message is actually received. A default implementation allows the payload stored as a std::string, but a specialized message class can be used for sending objects of a different type. When constructing a message by using the functionality provided by the Port class, this happens automatically. When receiving messages, the free function template is provided to extract the object from the message.\\
For example:
\begin{lstlisting}[language=C++,basicstyle=\small\color{black}]
//initialization of necessary objects is left out.
double value;
n_model::t_portptr port;

//create messages that contain a double
auto msgVector = port->createMessages(value);

//say we receive this message somewhere else
n_network::t_msgptr received =  msgVector[0];

//retrieve the data when receiving the message
const double& data = n_network::getMsgPayload<double>(received);

//Assuming that no Z function was applied to the message.
assert(value == data);
\end{lstlisting}

@@

	\item crash safety. The logger will catch the following signals and flush all remaining output before exiting the program:

@@

			\item \emph{SIGSEGV} Segmentation fault, sent by the operating system.
			\item \emph{SIGTERM} Termination request, sent by the program.
			\item \emph{SIGABRT} Abort --- abnormal termination, e.g. when an assertion fails.
			\item \emph{SIGINT} Interrupt, used for catching crtl+C, which is useful for debugging deadlocks.

@@

\chapter{Performance Analysis}
Whenever we made big design/architecture decisions, we first wrote some prototyping testcode to prove the viability (e.g. Network, Tracing, Logger).
\section{First comparison}
We use perf to get statistically sound benchmarks. The command run was :
\lstinline!$perf stat -r {rounds} {command}!\\

>>>>

\section{Messaging Size}
A message is constructed once, and after that never copied. Messages are sent and received by reference to smart pointer, incurring a size cost of (on 64-bit platforms) 128bit. The payload (and its size) is irrelevant to the simulation up to the point where the message is actually received. A default implementation allows the payload stored as a std::string, but this can be overridden by way of templated code. %TODO Stijn.

@@

It therefore lacks certain key features such as

@@

	\item crash safe
	\item custom assert that will log an error before shutting down

@@

Chances are that we will wait with implementing these features until we actually need them.
\chapter{Performance Analysis}
Whenever we made big design/architecture decisions, we first wrote some prototyping testcode to prove the viability (e.g. Network, Tracing, Logger).
\section{First comparison}
We use perf to get statistically sound benchmarks. The command run was :
\lstinline!$perf stat -r {rounds} {command}!\\
